Double trouble: Terrestrial ectortherm populations have both reduced opportunity for selection and physiological plasticity

### 2023-01-12 ms.rmd
Update to function script. Removed unecessary code. Fixed a rendering bug for inline code

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, cache = TRUE, warning = FALSE, tidy = TRUE, fig.width = 10)
## numbers >= 10^5 will be denoted in scientific notation,		  ## numbers >= 10^5 will be denoted in scientific notation,
  ## and rounded to 2 digits		  ## and rounded to 2 digits
  options(digits = 2)

@@

      # Do a tree check with original data
          tree_checks(data_long, tree, dataCol = "species_full", type = "checks")

@@

# Check that taxa dropped
  tree_checks(data_long, tree, dataCol = "species_full", type = "checks")

@@

Most of the effect size estimates came from measurements of metabolic rates (both resting and maximal -- $N_{species}$ = `r mr <- traits_all %>% filter(trait_category %in% c("rest_MR", "max_MR")); sum(mr[,"spp_n"])`, $N_{effects}$ = `r sum(mr[,"k"])`, considering acute and acclimation effects together), metabolic enzymes ($N_{species}$ = `r me <- traits_all %>% filter(trait_category %in% c("metabolic_enzyme", "ATPase")); me[,"spp_n"]`, $N_{effects}$ = `r me[,"k"]`) and whole-organism performance traits (i.e., sprint speed and endurance -- $N_{species}$ = `r per <- traits_all %>% filter(trait_category %in% c("sprint", "endurance")); sum(per[,"spp_n"])`, $N_{effects}$ = `r sum(per[,"k"])`).

>>>>

```{r setup, echo = FALSE, results="hide"}
knitr::opts_chunk$set(echo = FALSE, cache = TRUE, message = FALSE, warning = FALSE, tidy = TRUE, fig.width = 10)
## numbers >= 10^5 will be denoted in scientific notation,		  ## numbers >= 10^5 will be denoted in scientific notation,
  ## and rounded to 2 digits		  ## and rounded to 2 digits
  options(digits = 2)

@@

      # Do a tree check with original data
        #  tree_checks(data_long, tree, dataCol = "species_full", type = "checks")

@@

# Check that taxa dropped
 # tree_checks(data_long, tree, dataCol = "species_full", type = "checks")

@@

Most of the effect size estimates came from measurements of metabolic rates (both resting and maximal -- $N_{species}$ = `r mr <- traits_all %>% filter(trait_category %in% c("rest_MR", "max_MR")); sum(mr[,"spp_n"])`, $N_{effects}$ = `r sum(mr[,"k"])`, considering acute and acclimation effects together), metabolic enzymes ($N_{species}$ = `r me <- traits_all %>% filter(trait_category %in% c("metabolic_enzyme", "ATPase")); sum(me[,"spp_n"])`, $N_{effects}$ = `r me <- traits_all %>% filter(trait_category %in% c("metabolic_enzyme", "ATPase")); sum(me[,"k"])`) and whole-organism performance traits (i.e., measures of speed and endurance -- $N_{species}$ = `r per <- traits_all %>% filter(trait_category %in% c("sprint", "endurance")); sum(per[,"spp_n"])`, $N_{effects}$ = `r per <- traits_all %>% filter(trait_category %in% c("sprint", "endurance")); sum(per[,"k"])`).
